---
title: "Untitled"
author: "Richard J. Telford"
date: "8/27/2020"
output: pdf_document
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

#set default theme
theme_set(theme_bw())
```

## Methods

### Software

All analyses were done in R v. `r getRversion()` [@R] and used
vegan v. `r packageVersion("vegan")` [@vegan] for ordination,
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse] for data manipulation.
Packages drake v. `r packageVersion("drake")` [@drake], 
rmarkdown `r packageVersion("rmarkdown")` [@rmarkdown1] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/Lygra_traits/tree/Drake](https://github.com/richardjtelford/Lygra_traits/tree/Drake).

## Results

```{r nmds-plot, fig.cap = "NMDS"}
readd(nmds_plot)
```

```{r calluna-cover-plot, fig.cap = "Changes of _Calluna_ cover over time by health status. Sites are arranged from north-south."}
readd(calluna_cover_plot)
```

```{r community-group-plot, fig.cap = "Changes of community cover over time by taxonomic group. Sites are arranged from north-south."}
readd(community_group_cover)
```

```{r species_ordination_plot, fig.cap = "Too many species"}
readd(nmds_species_plot)
```

## References
