---
title: "Untitled"
author: "Richard J. Telford"
date: "8/27/2020"
output: pdf_document
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#set default theme
theme_set(theme_bw())
```

## Methods

```{r map, fig.cap = "Site map"}
readd(map)
```

```{r site-table}
loadd(site_data)
site_data %>% 
  select(-Site) %>% 
  relocate(code) %>% 
  rename(Code = code) %>% 
  knitr::kable(caption = "Sites")

```


### Software

All analyses were done in R v. `r getRversion()` [@R] and used
vegan v. `r packageVersion("vegan")` [@vegan] for ordination,
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse] for data manipulation.
Packages drake v. `r packageVersion("drake")` [@drake], 
rmarkdown `r packageVersion("rmarkdown")` [@rmarkdown1] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/Lygra_traits/tree/Drake](https://github.com/richardjtelford/Lygra_traits/tree/Drake).

## Results

```{r pca-plot, fig.cap="PCA of square root transformed cover"}
readd(PCA_plot)
```

```{r pca-sceeplot, fig.cap="Screeplot. Broken stick not meaningful with these data - probably because of the clustered data."}
screeplot(readd(PCA))
```


```{r nmds-plot, fig.cap = "NMDS"}
readd(nmds_plot)
```

```{r species_ordination_plot, fig.cap = "Too many species"}
readd(nmds_species_plot)
```

```{r calluna-cover-plot, fig.cap = "Changes of _Calluna_ cover over time by health status. Sites are arranged from north-south."}
readd(calluna_cover_plot)
```

```{r community-group-plot, fig.cap = "Changes of community cover over time by taxonomic group. Sites are arranged from north-south."}
readd(community_group_cover)
```

```{r seedling-plot, fig.cap = "Number of _Calluna_ seedlings over time in burnt plots.", fig.width = 80/25.4}
readd(seedling_plot)
```

## Proportion Dead

```{r dead-damaged-latitude, fig.cap="Proportion _Calluna_ dead (crosses, dotted red line),  damaged (open symbols, dashed blue line) or healthy (solid symbols, solid green line) in 2016 against Latitude. "}
  readd(dead_damage_lat_plot)
```


```{r dead-aspect, fig.cap = "Proportion _Calluna_ dead, damaged or healthy aspect"}
  readd(dead_north_plot)
```


```{r dead-depth, fig.cap = "Proportion _Calluna_ dead, damaged or healthy  against mean peat depth"}
  readd(dead_depth_plot)
```


```{r dead-slope, fig.cap = "Proportion _Calluna_ dead, damaged or healthy against slope"}
  readd(dead_slope_plot)
```



## Weather plot

```{r weather-plot, fig.cap = "Air temperature and relative humidity for January and February 2014"}
  readd(weather_plot)
```

## Climate plot

```{r climate-plot, fig.cap = "Mean relative humidity for January and February at the nearest weather station to each field site. The black bar represents the 2014 condtions."}
readd(climate_plot)
```



## References
