---
title: Recovery of coastal heathland after drought
author: "Richard J. Telford"
date: today
format: pdf
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
execute: 
  error: true
  echo: false
---

```{r}
#| label: setup
#| include: false

library(targets)
library(tidyverse)
library(vegan)
library(patchwork)

# force dependency on bibliography
tar_read(biblio2)

# set default theme
theme_set(theme_bw()+ 
            theme(panel.grid = element_blank()))
```

## Methods

```{r}
#| label: fig-map
#| fig-cap: Site map
theme_set(theme_bw())
tar_read(map)
theme_set(theme_bw() + 
            theme(panel.grid = element_blank()))
```



```{r}
#| label: tbl-sites
#| tbl-cap: Sites
tar_load(site_data)
site_data |>
  select(-Site) |>
  relocate(code) |>
  rename(Code = code) |>
  gt::gt() |>
  gt::fmt_number(c("Latitude", "Longitude"), decimals = 2)
```

### Statistical analysis

Mixed effect models were used to regress the proportion dead _Calluna_ in 2016 against drought severity (estimated as January 2014 relative humidity) and local factors (soil depth and aspect),
cover of regenerating _Calluna_ in burnt plots against time and latitude,
seedling number in burnt plots against latitude,
Except for seedling number which assumed a negative binomial distribution, all models assumed a Gaussian error distribution.

Ordinations were performed on all taxa with more than two occurrences. 
For detrended correspondence analysis / principal components analysis / correspondence analysis, taxon abundances were square root transformed.

### Software

All analyses were done in R v. `r getRversion()` [@R] and used
vegan v. `r packageVersion("vegan")` [@vegan] for ordination,
lme4 v. `r packageVersion("lme4")` [@lme4] and lmerTest v. `r packageVersion("lmerTest")` [@lmerTest] to fit mixed effect models
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse] for data manipulation.
Packages targets v. `r packageVersion("targets")` [@targets], 
quarto `r packageVersion("quarto")` [@quarto] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/Lygra_traits/tree/Drake](https://github.com/richardjtelford/Lygra_traits/tree/Drake).

## Results

### decorana

```{r}
#| label: dca

tar_load(pca_plots)
pca_plots$DCA
```

First axis is long - suggests we should be using CA or nmds.

If the burnt and unburnt plot are analysed separately, the length of the first DCA axis is 3.6 and 2.6 respectively.  


### pca
```{r}
#| label: fig-pca-plot
#| fig-cap: PCA of square root transformed cover
pca_plots$pca_plot
```

```{r}
#| label: fig-pca-plot-b
#| fig-cap: PCA of square root transformed cover v2
pca_plots$pca_plot_b
```
```{r}
#| label: fig-pca-plot-c
#| fig-cap: PCA of square root transformed cover v3
pca_plots$pca_plot_c
```


```{r}
#| label: fig-pca-sceeplot
#| fig-cap: Screeplot. Broken stick not meaningful with these data - probably because
#|   of the clustered data.
screeplot(pca_plots$PCA)
```

```{r}
#| label: fig-species_PCA_plot
#| fig-cap: Badly behaved species
pca_plots$PCA_species_plot
```

I think the pca look so good because they are dominated by changes of total cover in vegetation after burning, and not compositional changes.
As such the pca is just another way to present the cover bar charts.

### ca

```{r}
#| label: fig-ca-plot
#| fig-cap: CA of square root transformed cover
tar_load(ca_plots)
ca_plots$ca_plot
```

```{r}
#| label: fig-ca-plot-b
#| fig-cap: CA of square root transformed cover v2
ca_plots$ca_plot_b
```
```{r}
#| label: fig-ca-plot-c
#| fig-cap: CA of square root transformed cover v3
ca_plots$ca_plot_c
```





```{r}
#| label: fig-species_CA_plot
#| fig-cap: Badly behaved species
ca_plots$ca_species_plot
```

ca are mostly ignoring the changes in total cover, focusing on the relative abundance. 
They look messy.

### nmds

```{r}
#| label: fig-nmds-plot
#| fig-cap: NMDS
tar_load(nmds_plots)
nmds_plots$nmds_plot
```

```{r}
#| label: fig-species_ordination_plot
#| fig-cap: Too many species
nmds_plots$nmds_species_plot
```

NMDS also looks messy.

### cover bar plots

```{r}
#| label: fig-calluna-cover-plot
#| fig-cap: Changes of _Calluna_ cover over time by health status. Sites are arranged
#|   from north-south.
#|   Red-black line indicates the timing of the burning in the burnt plots.
#| fig-height: !expr 13/2.54
#| fig-width: !expr 12/2.54
tar_read(calluna_cover_plot)
```

```{r}
#| label: fig-community-group-plot
#| fig-cap: Changes of community cover over time by taxonomic group. 
#|   Sites are arranged from north-south.
#|   Red-black line indicates the timing of the burning in the burnt plots.
#| fig-height: !expr 20/2.54
#| fig-width: !expr 15/2.54
tar_read(community_group_cover_plot)
```

```{r}
#| label: fig-seedling-plot
#| fig-cap: Number of _Calluna_ seedlings over time in burnt plots.
#| fig-width: !expr 80/25.4
tar_read(seedling_plot)
```

## Proportion Dead

```{r}
#| label: fig-dead-damaged-latitude
#| fig-cap: Proportion _Calluna_ dead,  damaged or healthy in 2016 against relative humidity.
#|   Lines are loess smoothers.
tar_read(dead_damage_lat_plot)
```


```{r}
#| label: fig-dead-aspect
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy aspect
tar_read(dead_north_plot)
```


```{r}
#| label: fig-dead-depth
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy  against mean peat depth
tar_read(dead_depth_plot)
```


```{r}
#| label: fig-dead-slope
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy against slope
tar_read(dead_slope_plot)
```



## Weather plot

```{r}
#| label: fig-weather-plot
#| fig-cap: Air temperature and relative humidity for January and February 2014
tar_read(weather_plot)
```

## Climate plot

```{r}
#| label: fig-climate-plot
#| fig-cap: Mean precipitation, temperature and relative humidity for January at the
#|   nearest weather station to each field site. The black arrow indicates the 2014 condtions.
#|   2014 precipitation data are missing for site _F_.
tar_read(climate_plot)
```

## Models

### Seedling burnt vs unburnt

```{r}
tar_load(seedling_model)
seedling_model$treatment |> summary()

broom.mixed::augment(seedling_model$treatment, newdata = tibble(treatment = c("Burnt", "Unburnt")), re.form = NA) |> 
  mutate(mean = exp(.fitted)) |> 
  select(treatment, mean)
```

### Seedling abundance against latitude. 

Mixed effect model with negative binomial distribution, random effect is plot nested in site.

```{r}
seedling_model$latitude |> summary()
```

### Proportion dead by various predictors

```{r}
#| echo: true
# Latitude as a proxy for drought severity

summary(tar_read(mod_lat))

# RH
summary(tar_read(mod_RH))

# RH and peat depth
tar_read(mod_RH_depth) |> summary()

# RH and aspect
tar_read(mod_RH_north) |> summary()
```

### Recovery of Calluna in burnt plots

```{r}
#| echo: true
# year
summary(tar_read(burnt_year_mod))

# year + latitude
summary(tar_read(burnt_yearlat_mod))

# year * latitude (interaction not significant - too complex model)
summary(tar_read(burnt_yearxlat_mod))

# Year + latitude + depth
summary(tar_read(burnt_yeardepth_mod))
# Year + latitude + aspect
summary(tar_read(burnt_yearnorth_mod))
```


## References
