---
title: "Untitled"
author: "Richard J. Telford"
date: "8/27/2020"
output: pdf_document
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# library(drake)
# library(tidyverse)
# library(vegan)

#set default theme
theme_set(theme_bw())
```

## Methods

```{r map, fig.cap = "Site map"}
readd(map)
```

```{r site-table}
loadd(site_data)
site_data %>% 
  select(-Site) %>% 
  relocate(code) %>% 
  rename(Code = code) %>% 
  knitr::kable(caption = "Sites")

```

### Statistical analysis

Mixed effect models were used to regress the proportion dead _Calluna_ in 2016 against drought severity (estimated as January 2014 relative humidity) and local factors (soil depth and aspect),
cover of regenerating _Calluna_ in burnt plots against time and latitude,
seedling number in burnt plots against latitude,
Except for seedling number which assumed a negative binomial distribution, all models assumed a Gaussian error distribution.


### Software

All analyses were done in R v. `r getRversion()` [@R] and used
vegan v. `r packageVersion("vegan")` [@vegan] for ordination,
lme4 v. `r packageVersion("lme4")` [@lme4] and lmerTest v. `r packageVersion("lmerTest")` [@lmerTest] to fit mixed effect models
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse] for data manipulation.
Packages drake v. `r packageVersion("drake")` [@drake], 
rmarkdown `r packageVersion("rmarkdown")` [@rmarkdown1] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/Lygra_traits/tree/Drake](https://github.com/richardjtelford/Lygra_traits/tree/Drake).

## Results

```{r pca-plot, fig.cap="PCA of square root transformed cover"}
readd(pca_plot)
```

```{r pca-plot-b, fig.cap="PCA of square root transformed cover v2"}
readd(pca_plot_b)
```
```{r pca-plot-c, fig.cap="PCA of square root transformed cover v3"}
readd(pca_plot_c)
```



```{r pca-plot13, fig.cap="PCA of square root transformed cover, axes 1 & 3"}
readd(PCA13_plot)
```


```{r pca-sceeplot, fig.cap="Screeplot. Broken stick not meaningful with these data - probably because of the clustered data."}
screeplot(readd(PCA))
```

```{r species_PCA_plot, fig.cap = "Badly behaved species"}
readd(PCA_species_plot)
```


```{r nmds-plot, fig.cap = "NMDS"}
readd(nmds_plot)
```

```{r species_ordination_plot, fig.cap = "Too many species"}
readd(nmds_species_plot)
```

```{r calluna-cover-plot, fig.cap = "Changes of _Calluna_ cover over time by health status. Sites are arranged from north-south.", fig.height = 13/2.54, fig.width = 12/2.54}
readd(calluna_cover_plot)
```

```{r community-group-plot, fig.cap = "Changes of community cover over time by taxonomic group. Sites are arranged from north-south.", fig.height = 13/2.54, fig.width = 12/2.54}
readd(community_group_cover)
```

```{r seedling-plot, fig.cap = "Number of _Calluna_ seedlings over time in burnt plots.", fig.width = 80/25.4}
readd(seedling_plot)
```

## Proportion Dead

```{r dead-damaged-latitude, fig.cap="Proportion _Calluna_ dead,  damaged or healthy in 2016 against relative humidity. Lines are loess smoothers."}
  readd(dead_damage_lat_plot)
```


```{r dead-aspect, fig.cap = "Proportion _Calluna_ dead, damaged or healthy aspect"}
  readd(dead_north_plot)
```


```{r dead-depth, fig.cap = "Proportion _Calluna_ dead, damaged or healthy  against mean peat depth"}
  readd(dead_depth_plot)
```


```{r dead-slope, fig.cap = "Proportion _Calluna_ dead, damaged or healthy against slope"}
  readd(dead_slope_plot)
```



## Weather plot

```{r weather-plot, fig.cap = "Air temperature and relative humidity for January and February 2014"}
  readd(weather_plot)
```

## Climate plot

```{r climate-plot, fig.cap = "Mean precipitation, temperature and relative humidity for January at the nearest weather station to each field site. The black arrow indicates the 2014 condtions. 2014 precipitation data are missing for site _f_."}
readd(climate_plot)
```

## Models

### Seedling abundance against latitude. 

Mixed effect model with negative binomial distribution, random effect is plot nested in site.
Year is a fixed effect as too few years to use as a random effect. 
(Model is singular, probably because all values within some groups are zero. )

```{r}
readd(seedling_model) %>% summary()
```

### Proportion dead by various predictors

```{r echo= TRUE}
# Latitude as a proxy for drought severity

summary(readd(mod_lat))

# RH
summary(readd(mod_RH))

# RH and peat depth
readd(mod_RH_depth) %>% summary()

# RH and aspect
readd(mod_RH_north) %>% summary()


```

### Recovery of Calluna in burnt plots

```{r echo=TRUE}
#year
summary(readd(burnt_year_mod))

# year + latitude
summary(readd(burnt_yearlat_mod))

# year * latitude (interaction not significant - too complex model)
summary(readd(burnt_yearxlat_mod))

# Year + latitude + depth
summary(readd(burnt_yeardepth_mod))
# Year + latitude + aspect
summary(readd(burnt_yearnorth_mod))

```


## References
