---
title: Recovery of coastal heathland after drought
author: "Richard J. Telford"
date: today
format: pdf
classoption: a4paper
bibliography: Rmd/TDT2.bib
csl: Rmd/elsevier-harvard_rjt.csl
execute: 
  error: true
---

```{r}
#| label: setup
#| include: false

library(targets)
library(tidyverse)
library(vegan)
library(patchwork)

# set default theme
theme_set(theme_bw()+ 
            theme(panel.grid = element_blank()))
```

## Methods

```{r}
#| label: fig-map
#| fig-cap: Site map
theme_set(theme_bw())
tar_read(map)
theme_set(theme_bw() + 
            theme(panel.grid = element_blank()))
```



```{r}
#| label: tbl-sites
#| tbl-cap: Sites
tar_load(site_data)
site_data |>
  select(-Site) |>
  relocate(code) |>
  rename(Code = code) |>
  gt::gt() |>
  gt::fmt_number(c("Latitude", "Longitude"), decimals = 2)
```

### Statistical analysis

Mixed effect models were used to regress the proportion dead _Calluna_ in 2016 against drought severity (estimated as January 2014 relative humidity) and local factors (soil depth and aspect),
cover of regenerating _Calluna_ in burnt plots against time and latitude,
seedling number in burnt plots against latitude,
Except for seedling number which assumed a negative binomial distribution, all models assumed a Gaussian error distribution.


### Software

All analyses were done in R v. `r getRversion()` [@R] and used
vegan v. `r packageVersion("vegan")` [@vegan] for ordination,
lme4 v. `r packageVersion("lme4")` [@lme4] and lmerTest v. `r packageVersion("lmerTest")` [@lmerTest] to fit mixed effect models
and tidyverse v. `r packageVersion("tidyverse")` [@tidyverse] for data manipulation.
Packages targets v. `r packageVersion("targets")` [@targets], 
quarto `r packageVersion("quarto")` [@quarto] and
renv v. `r packageVersion("renv")` [@renv] were used to ensure reproducibility.
Code to reproduce all the analyses is archived at [https://github.com/richardjtelford/Lygra_traits/tree/Drake](https://github.com/richardjtelford/Lygra_traits/tree/Drake).

## Results

```{r}
#| label: dca

tar_load(pca_plots)
pca_plots$DCA
```


```{r}
#| label: fig-pca-plot
#| fig-cap: PCA of square root transformed cover
pca_plots$pca_plot
```

```{r}
#| label: fig-pca-plot-b
#| fig-cap: PCA of square root transformed cover v2
pca_plots$pca_plot_b
```
```{r}
#| label: fig-pca-plot-c
#| fig-cap: PCA of square root transformed cover v3
pca_plots$pca_plot_c
```



```{r}
#| label: fig-pca-plot13
#| fig-cap: PCA of square root transformed cover, axes 1 & 3
pca_plots$PCA13_plot
```


```{r}
#| label: fig-pca-sceeplot
#| fig-cap: Screeplot. Broken stick not meaningful with these data - probably because
#|   of the clustered data.
screeplot(pca_plots$PCA)
```

```{r}
#| label: fig-species_PCA_plot
#| fig-cap: Badly behaved species
pca_plots$PCA_species_plot
```


```{r}
#| label: fig-nmds-plot
#| fig-cap: NMDS
tar_load(nmds_plots)
nmds_plots$nmds_plot
```

```{r}
#| label: fig-species_ordination_plot
#| fig-cap: Too many species
nmds_plots$nmds_species_plot
```

```{r}
#| label: fig-calluna-cover-plot
#| fig-cap: Changes of _Calluna_ cover over time by health status. Sites are arranged
#|   from north-south.
#| fig-height: !expr 13/2.54
#| fig-width: !expr 12/2.54
tar_read(calluna_cover_plot)
```

```{r}
#| label: fig-community-group-plot
#| fig-cap: Changes of community cover over time by taxonomic group. Sites are arranged from north-south.
#| fig-height: !expr 20/2.54
#| fig-width: !expr 15/2.54
tar_read(community_group_cover_plot)
```

```{r}
#| label: fig-seedling-plot
#| fig-cap: Number of _Calluna_ seedlings over time in burnt plots.
#| fig-width: !expr 80/25.4
tar_read(seedling_plot)
```

## Proportion Dead

```{r}
#| label: fig-dead-damaged-latitude
#| fig-cap: Proportion _Calluna_ dead,  damaged or healthy in 2016 against relative humidity.
#|   Lines are loess smoothers.
tar_read(dead_damage_lat_plot)
```


```{r}
#| label: fig-dead-aspect
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy aspect
tar_read(dead_north_plot)
```


```{r}
#| label: fig-dead-depth
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy  against mean peat depth
tar_read(dead_depth_plot)
```


```{r}
#| label: fig-dead-slope
#| fig-cap: Proportion _Calluna_ dead, damaged or healthy against slope
tar_read(dead_slope_plot)
```



## Weather plot

```{r}
#| label: fig-weather-plot
#| fig-cap: Air temperature and relative humidity for January and February 2014
tar_read(weather_plot)
```

## Climate plot

```{r}
#| label: fig-climate-plot
#| fig-cap: Mean precipitation, temperature and relative humidity for January at the
#|   nearest weather station to each field site. The black arrow indicates the 2014 condtions.
#|   2014 precipitation data are missing for site _F_.
tar_read(climate_plot)
```

## Models

### Seedling abundance against latitude. 

Mixed effect model with negative binomial distribution, random effect is plot nested in site.
Year is a fixed effect as too few years to use as a random effect. 
(Model is singular, probably because all values within some groups are zero. )

```{r}
tar_read(seedling_model) |> summary()
```

### Proportion dead by various predictors

```{r}
#| echo: true
# Latitude as a proxy for drought severity

summary(tar_read(mod_lat))

# RH
summary(tar_read(mod_RH))

# RH and peat depth
tar_read(mod_RH_depth) |> summary()

# RH and aspect
tar_read(mod_RH_north) |> summary()
```

### Recovery of Calluna in burnt plots

```{r}
#| echo: true
# year
summary(tar_read(burnt_year_mod))

# year + latitude
summary(tar_read(burnt_yearlat_mod))

# year * latitude (interaction not significant - too complex model)
summary(tar_read(burnt_yearxlat_mod))

# Year + latitude + depth
summary(tar_read(burnt_yeardepth_mod))
# Year + latitude + aspect
summary(tar_read(burnt_yearnorth_mod))
```


## References
